Updated Constraints on Self-Interacting Dark Matter from Supernova 1987A

### 2017-06-08 draft.tex
removed comment now that figure was fixed.
added comment

\begin{figure*}[th]
\includegraphics[width=14cm]{compiledbounds_edited.pdf}
\caption{
Constraints on dark photon models. The constraint scales according to the assumed, maximal energy loss rate of $\epsilon_{\mathrm{A}'} = 10^{19}\, \mathrm{erg}\, \mathrm{g}^{-1}\ \mathrm{s}^{-1}$ as shown on the vertical axis label. Our primary result is the excluded region 
in the $\varepsilon$-$m_{\mathrm{A'}}$ plane shaded in blue. The red curve is our attempt to reproduce exactly Ref.~\cite{dent_etal12}, while the black curve is Ref.~\cite{dent_etal12} but with the correct luminosity constraint.  The purple curve was computed by using the SRA and fixing the cross section through a polynomial fit to nuclear scattering data (e.g., see \cite{rrapaj_reddy16}), while the green curve uses the SRA of the OPE result.  \akl{Please change vertical axis label by $\varepsilon_{\mathrm A'} \to \epsilon_{\mathrm A'}$ and remove parenthesis. On horizontal axis, put prime over A, not next to the A.}
}
\label{fig:constraint}
\end{figure*}

@@

Finally, we note that the interior temperature and density within the progenitor of SN1987A remain 
uncertain at least at the level of tens of percent \citep[e.g.][]{perego15,farmer16}. This is well worth 
noting because the constraints one derives using the techniques in this work or similar techniques 
are quite sensitive to the properties of the SN1987A core, particularly the core temperature. Though 
we do not show this result explicitly \akl{Seems to me we should...} 
we have replicated our calculations for shifts in core temperature 
of $\pm 5\, \mathrm{MeV}$ and find that the boundaries of the excluded region shift by a factor of $\sim 2-3$ at low 
mass ($m_{\mathrm{A}'} \lesssim T$ where $T = 30\, \mathrm{MeV}$ in our fiducial calculation, following 
work or previous authors) and considerably more at high mass. 
We conclude that the differences among theoretical techniques for 
computing the excluded region (OPE, EFT, SRA, ...) lead to uncertainties that are of the same order or 
smaller than the uncertainty in the excluded region induced by our limited knowledge of the 
properties of the SN1987A progenitor interior. The excluded regions we and other authors delineate 
should be considered to be uncertain by a factor or $\sim 3$. Refining the theoretical approach to this 
problem is therefore unwarranted until a breakthrough in our understanding of the interior of the 
SN1987A progenitor is achieved.

>>>>

\begin{figure*}[th]
\includegraphics[width=14cm]{compiledbounds_edited.pdf}
\caption{
Constraints on dark photon models. The constraint scales according to the assumed, maximal energy loss rate of $\epsilon_{\mathrm{A}'} = 10^{19}\, \mathrm{erg}\, \mathrm{g}^{-1}\ \mathrm{s}^{-1}$ as shown on the vertical axis label. Our primary result is the excluded region 
in the $\varepsilon$-$m_{\mathrm{A'}}$ plane shaded in blue. The red curve is our attempt to reproduce exactly Ref.~\cite{dent_etal12}, while the black curve is Ref.~\cite{dent_etal12} but with the correct luminosity constraint.  The purple curve was computed by using the SRA and fixing the cross section through a polynomial fit to nuclear scattering data (e.g., see \cite{rrapaj_reddy16}), while the green curve uses the SRA of the OPE result.
}
\label{fig:constraint}
\end{figure*}

@@

Finally, we note that the interior temperature and density within the progenitor of SN1987A remain 
uncertain at least at the level of tens of percent \citep[e.g.][]{perego15,farmer16}. This is well worth 
noting because the constraints one derives using the techniques in this work or similar techniques 
are quite sensitive to the properties of the SN1987A core, particularly the core temperature. Though 
we do not show this result explicitly \akl{Seems to me we should...  Also, change horizontal label $M_{A'} \to M_{\mathrm{A}'}$.} 
we have replicated our calculations for shifts in core temperature 
of $\pm 5\, \mathrm{MeV}$ and find that the boundaries of the excluded region shift by a factor of $\sim 2-3$ at low 
mass ($m_{\mathrm{A}'} \lesssim T$ where $T = 30\, \mathrm{MeV}$ in our fiducial calculation, following 
work or previous authors) and considerably more at high mass. 
We conclude that the differences among theoretical techniques for 
computing the excluded region (OPE, EFT, SRA, ...) lead to uncertainties that are of the same order or 
smaller than the uncertainty in the excluded region induced by our limited knowledge of the 
properties of the SN1987A progenitor interior. The excluded regions we and other authors delineate 
should be considered to be uncertain by a factor or $\sim 3$. Refining the theoretical approach to this 
problem is therefore unwarranted until a breakthrough in our understanding of the interior of the 
SN1987A progenitor is achieved.
